Verifying Spatial Properties of Array Computations

### 2017-04-17 oopsla17/algorithms.tex
Add the missing step in inference

The final stage of inference is simply mapping interval schemes into region
constants. Each interval scheme is connected with \texttt{+} and each dimension
of the interval scheme is connected with \texttt{*}. The intervals at each
dimension are mapped to region constants using the bijection defined in
\Cref{sec:semantics}.

In the example, $[-1, 1] \times [0, 0]$ is mapped to \texttt{\stencil{c}{1}{1}{}
* \stencil{p}{2}{}{}} and $[0, 0] \times [-1, 1]$ is mapped to
\texttt{\stencil{p}{1}{}{} * \stencil{c}{2}{1}{}}, producing the overall
specification:
%
\begin{equation*}
  \texttt{stencil readOnce,} \;
  \stencil[s]{c}{1}{1}{} \texttt{*} \stencil[s]{p}{2}{}{} \; \texttt{+} \;
  \stencil[s]{p}{1}{}{}  \texttt{*} \stencil[s]{c}{2}{1}{}
\end{equation*}

>>>>

The final stage of inference is simply mapping interval schemes into region
constants. Each interval scheme is connected with \texttt{+}. Individual schemes
are decomposed using \Cref{lem:vector-intersect} such that each of the resulting
index schemes have all but one dimensions set to \interv{-\infty}{\infty}{}.
Each of these interval schemes are mapped to region constants using
\Cref{subfig:region-model} and connected with \texttt{*}.

In the example, $[-1, 1] \times [0, 0]$ is decomposed into $\interv{-1}{1}{}
\times \interv{-\infty}{\infty}{}$ and $\interv{-\infty}{\infty}{} \times
\interv{0}{0}{}$. These are then mapped to \texttt{\stencil{c}{1}{1}{}
* \stencil{p}{2}{}{}}. Decomposition of $[0, 0] \times [-1, 1]$ is similar. When
combined we obtain the following specification:
%
\begin{equation*}
  \texttt{stencil readOnce,} \;
  \stencil[s]{c}{1}{1}{} \texttt{*} \stencil[s]{p}{2}{}{} \; \texttt{+} \;
  \stencil[s]{p}{1}{}{}  \texttt{*} \stencil[s]{c}{2}{1}{}
\end{equation*}
